Aracna: An Open-Source Quadruped Platform for Evolutionary Robotics

### 2012-05-18 paper_aracna/main.tex
more writing...

In this paper we address these needs by introducing \emph{Aracna}, a low-cost, open-source hardware, easily customizable robot platform with non-intuitive walking
kinematics~(Figure 1). Aracna is the third quadruped robot developed for evolutionary learning algorithms by the Creative Machines Lab at Cornell University~\citep{HL, JY}. Like the previous QuadraTot robot design~\citep{yosinski2011gaits}, the body of Aracna is 3D printed, and the STL files are available online
%TODO: INSERT LINK
, meaning that other teams can easily customize the body's design. As in the previous two designs, each leg has a hip and knee joint controlled by two actuators. The original Creative
Machines Lab quadruped robot favored starfish-like movements~\citep{HL}. The second quadruped robot --- QuadraTot ---
developed spider-like movements, but was found to be limited by its
weight, such that the motors would overheat and timeout when trying to execute many commands~\citep{JY, Glette2012Evolution}. We designed Aracna to be able to produce fast, spider-like movements, yet be lightweight enough that the motors would not overheat. We also designed Aracna to be inexpensive: as described below, its overall price is under \$1,500  USD. In the following sections we describe the Aracna platform in more detail.

\section{Hardware}

\begin{figure}[t]
\begin{center}
\includegraphics[width=.23\textwidth]{fig3.pdf}
\includegraphics[width=.23\textwidth]{fig4.pdf}
\caption{Crank-rocker four-bar linkage controlling flexion/extension of
  the knee and hip joints. In both cases above, the input crank (link
  OA) is actuated by a servo, the rocker is the leg (link CB), and the
  fixed link is OC.}
\label{fig3}
\end{center}
\end{figure}

@@

The hardware of Aracna evolved from the previous Creative Machines Lab
quadruped robots. We kept the same two degree of freedom pitch joint
scheme but decreased the weight and constrained the movement of the
joints toward the goal of creating faster spider-like movement. To
prevent starfish-like movement, the legs were constrained. We designed
the robot with two four-bar mechanisms to drive the joints in each
leg. With a four-bar mechanism in place, the leg moves at a fraction
of the output angle of the actuator, giving the motor a relatively
larger mechanical advantage over the position of each leg.
Figure~\ref{fig3} shows the crank-rocker system, where the input crank
is actuated by a servo and the rocker is the leg. In this
configuration, we keep the servo motors contained in the center of the
robot, reducing both the inertia and mass of each leg. The four-bar
mechanisms satisfied the design goal of making a robot that had
non-traditional movements.  To make the robot
accessible as an open-source platform, it was designed to be 3D
printed. The 3D print files and CAD files can be accessed by the
public to be printed and, if desired, modified.

The robot is designed to be lightweight, because previous similar
robots may have been too heavy and underpowered to generate
interesting gaits. We use a single LiPo 11.1V battery to
power 8 Dynamixel AX-18 servo motors and an ArbotiX
microcontroller. The main processing occurs on an external computer,
which allows the robot to have cheaper and lighter components
on-board. The space in the center of the body houses the
battery to reduce material weight and cost. Aracna weighs 1.03 kg.
% 1034g

\begin{figure}[t]
\begin{center}
\includegraphics[width=\columnwidth]{fig5.jpg}
\caption{Rendered CAD model of Aracna.}
\label{fi52}
\end{center}
\end{figure}

@@

The software is open-sourced Python based on the
code developed for the QuadraTot platform \citep{JY}. All code is
available on the project website \citep{WEB}. We use an infrared light
emitting diode (LED) on the robot along with an external Nintendo Wii
remote to provide feedback of the distance traveled. The robot
receives feedback from the Wii remote and internal servo sensors and
then processes the information to send the next command to
the servos. The communication between the external control computer
and the ArbotiX on-board microcontroller occurs over wireless XBee.

\begin{figure}[t]
\begin{center}
\includegraphics[width=.37\textwidth]{fig2.jpg}
\caption{Robot printed as one piece with support material intact.}
\label{fig2}
\end{center}
\end{figure}

The Aracna may be 3D printed as a single part (Figure~\ref{fig2}). On
an Object Connex500 printer, the robot was completed in 26 hours,
using approximately 1000 g of model material and 1500 g of support
material. We estimated the cost of the printed parts to be \$410 by
using an estimated model material cost of \$1/4.5g and support
material cost of \$1/8g. This cost estimate is variable depending on
the type of material used. The robot has no removable printed parts
except for the battery cover. In the near future, we will make STL files
available for printing the robot as separate parts on
3D printers with smaller tray sizes. Printing the robot as separate parts
will also reduce the amount of support material needed, and thus the
overall cost. As shown in Table~\ref{tab:cost}, the total cost of the
Aracna is just under \$1500; these estimates are based on the material
calculations above and prices from trossenrobotics.com in March 2012.

\begin{table}[h]
\center{
\begin{tabular}{|c|c|}
\hline
Part & Cost\\
\hline\hline
3D Print Materials & \$410\\
ArbotiX Robocontroller Kit & \$189\\
Dynamixel AX-18A Robot Actuator (x8) & \$721\\
3S 11.1V 2000mAh Pro Lite LiPo Battery & \$73\\
LiPo Battery Balance Charger Kit & \$70\\
Cables, Connectors, Misc & \$28\\
\hline\hline
\bf Total & \bf \$1491\\
 \hline
\end{tabular}
}
\vskip 0.25cm
\caption{Estimated total cost. A complete parts list is on our website \citep{WEB}.}
\label{tab:cost}
\end{table}

>>>>

In this paper we address these needs by introducing \emph{Aracna}, a low-cost, open-source hardware, easily customizable robot platform with non-intuitive walking
kinematics~(Figure 1). Aracna is the third quadruped robot developed for evolutionary learning algorithms by the Creative Machines Lab at Cornell University~\citep{bongard2006resilient, yosinski2011gaits}. Like the most recent of the two previous designs, called QuadraTot~\citep{yosinski2011gaits}, the body of Aracna is 3D printed and the STL files are available online,
%TODO: INSERT LINK
meaning that other researchers can easily customize the body's design. As in the both previous designs, each leg has a hip and knee joint controlled by two actuators. The original Creative
Machines Lab quadruped robot favored starfish-like movements~\citep{bongard2006resilient}. The second quadruped robot --- QuadraTot ---
developed spider-like movements, but was found to be limited by its
weight, such that the motors would overheat and timeout when trying to execute many commands~\citep{yosinski2011gaits, Glette2012Evolution}. We designed Aracna to be able to produce fast, spider-like movements, yet be lightweight enough that the motors would not overheat. We also designed Aracna to be inexpensive: as described below, its overall price is under \$1,500  USD. In the following sections we describe the Aracna platform in more detail.

\section{Overall Hardware Design}

\begin{figure}[t]
\begin{center}
\includegraphics[width=\columnwidth]{fig5.jpg}
\caption{Rendered CAD model of Aracna.}
\label{cadModelOfRobot}
\end{center}
\end{figure}

@@

The hardware of Aracna was designed to improve upon the previous Creative Machines Lab
quadruped robots~\citep{bongard2006resilient, yosinski2011gaits}, while still qualitatively resembling those robots. Aracna is similar in that it has a body and four legs, with each leg having two joints that can pitch forward and back like knees~(Figure~\ref{cadModelOfRobot}).

One change was to constrain the movement of the
joints toward the goal of creating faster, spider-like movements. To
prevent starfish-like movements and instead encourage a walking gait with the robot body permanently off the ground, the legs were constrained such that they cannot straighten out and the knee cannot hyperextend.

Another change was to reduce the both the overall weight of the robot and the weight of each leg. Two previous studies that used the QuadraTot robot report that the motors quickly wore out and could not reliably execute the commands sent to them, likely because of both the overall weight of the QuadraTot and the fact that housing servos on the legs made them heavy~\citep{bongard2006resilient, yosinski2011gaits}. The weight of the robot's core was reduced in a number of ways.

Initially, we eliminated the QuadraTot's fit-PC, an onboard Linux computer weighing 370g, and replaced it with an ArbotiX microcontroller that weights only 47g. As a result, the main processing occurs on an external computer and commands are sent to Aracna wirelessly. This change, of course, comes of the cost of the robot being truly autonomous.

A second means of eliminating weight involved switching to a lighter battery. The QuadraTot had two 12V lithium-ion battery packs that weighted 140g each for a total of 280g. Aracna has a single lithium-polymer 11.1V battery that weighs SARA-TO-INSERT-WEIGHT. INSERT SENTENCE ON THE COST OF USING THE SMALLER BATTERY.

A major modification, targeted at reducing the weight of legs, was the use of two four-bar mechanisms to drive the joints in each
leg. This mechanism causes the controlled joint to move at a fraction
of the output angle of the actuator, giving the motor a relatively
larger mechanical advantage over the position of each leg.
Figure~\ref{crankRocker} shows the crank-rocker system, where the input crank
is actuated by a servo and the rocker is the leg. This
configuration allows the servo motors to be contained in the robot core, reducing both the inertia and mass of each leg. The weight of an Aracna leg is SARA-TO-INSERT compared to the 217g for a QuadraTot leg.

Combined, these changes to minimize weight led to a SARA-TO-INSERT percent reduction in weight of the robot. The QuadraTot weighs 1.88kg whereas Aracna weighs SARA-TO-INSERTkg

A final change was to upgrade the power of the servo motors in order to increase the ability of the robot to strike whichever configurations are specified by the learning algorithms. Specifically, we upgraded from Dynamixel AX 12+ motors to AX-18 motors, which provide INSERT-SENTENCE-ON-DIFFERENCE-IN-SERVO-POWER.

\section{3D Printed Body}

The body of Arcana takes advantage of 3D printing technology, also known as additive manufacturing, which generates physical objects from digital designs by building them up layer by layer~\citep{gibson2009additive, lipson2010factory}. The use of 3D printing means that other Aracna users can easily make copies of Aracna, either by having access to a 3D printer or via online 3D printing services such as Shapeways.com. Either option requires the 3D design files in the STereoLithography (STL) format, which we are publishing in the online support material for this paper~\citep{WEB}. Moreover, to catalyze innovation in this open-source hardware project, we are also providing the source files for the SolidWorks computer-aided-design program, because it is easier to modify a design with the original source files than with STL files. It should thus be easy for future Aracna users to improve or alter the design and quickly obtain a physical instantiation of the design. Importantly, the use of 3D printing eliminates the need to know how to machine parts, allowing many more researchers to participate in using physical robot morphologies that they design themselves. These ideas are in line with a broader trend toward enabling non-technical users to design and manufacture physical objects~\citep{clune2011objects, clune2011endless, lipson2010factory}.

An initial version of Aracna was designed to be printed in one piece~(Figure~\ref{notYetCleanedOnePieceRobot}). However, if one part of the robot became damaged, an entire new robot had to be reprinted, which took over 26 hours and cost roughly \$410 USD on an Object Connex500 printer. To make repairing the robot easier, cheaper, and quicker, Aracna was redesigned to be modular. It consists of INSERT pieces--four legs and the core--that can be separately 3D printed~(Figure~REFERENCE FIGURES OF THE NEW DESIGN PRINTED). Printing a leg takes INSERT hours and costs INSERT. Printing the core takes INSERT hours and costs INSERT. All INSERT Aracna pieces can still be printed as one print job, with an overall time of INSERT and cost of INSERT. These figures are based on Aracna's use of  approximately INSERT g of rigid material and INSERT g of support
material, and current material costs of 4.5g per USD and 8g per USD for rigid and support material, respectively. This cost estimate is variable depending on
the type of material used. Table~\ref{tab:cost} outlines the total estimated cost of Aracna, which is just under \$1500, including its off-the-shelf electronic components.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.37\textwidth]{fig2.jpg}
\caption{Robot printed as one piece with support material intact.}
\label{notYetCleanedOnePieceRobot}
\end{center}
\end{figure}

\section{Control}

The four-bar
mechanisms also satisfied the design goal of making a robot that had
non-traditional movements. There is not a one-to-one mapping between the servo output and the movement of the joint that servo controls. Figure INSERT displays the resulting joint angle as a function of the angle the servo is commanded to.

\begin{figure}[t]
\begin{center}
\includegraphics[width=.23\textwidth]{fig3.pdf}
\includegraphics[width=.23\textwidth]{fig4.pdf}
\caption{Crank-rocker four-bar linkage controlling flexion/extension of
  the knee and hip joints. In both cases above, the input crank (link
  OA) is actuated by a servo, the rocker is the leg (link CB), and the
  fixed link is OC.}
\label{crankRocker}
\end{center}
\end{figure}

% 1034g

@@

The software is open-sourced Python based on the
code developed for the QuadraTot platform \citep{yosinski2011gaits}. All code is
available on the project website \citep{WEB}. We use an infrared light
emitting diode (LED) on the robot along with an external Nintendo Wii
remote to provide feedback of the distance traveled. The robot
receives feedback from the Wii remote and internal servo sensors and
then processes the information to send the next command to
the servos. The communication between the external control computer
and the ArbotiX on-board microcontroller occurs over wireless XBee.

\begin{table}[h]
\center{
\begin{tabular}{|c|c|}
\hline
Part & Cost\\
\hline\hline
3D Print Materials & \$410\\
ArbotiX Robocontroller Kit & \$189\\
Dynamixel AX-18A Robot Actuator (x8) & \$721\\
3S 11.1V 2000mAh Pro Lite LiPo Battery & \$73\\
LiPo Battery Balance Charger Kit & \$70\\
Cables, Connectors, Misc & \$28\\
\hline\hline
\bf Total & \bf \$1491\\
 \hline
\end{tabular}
}
\vskip 0.25cm
\caption{Estimated total cost. The cost of components and printing material reflect market prices from March 2012. A complete parts list is on our website \citep{WEB}.}
\label{tab:cost}
\end{table}
